\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{calc}
\usepackage{setspace}
\usepackage{fixltx2e}
\usepackage{multicol}
\usepackage[english]{babel}
\usepackage{color}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage{marvosym}
\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.75in,nohead,nofoot]{geometry}
\usepackage{needspace}

\newcommand{\head}[1]{\needspace{6em}\begin{center}{\large{\textbf{\sc{#1}}}}\nopagebreak\end{center}}
\newcommand{\expertise}[2]{\item[#1:] #2}
\newcommand{\jobheld}[2]{\textbf{#1\hfill #2}\nopagebreak}
\newcommand{\clientwork}[3]{\textbf{#1\hfill#3\hfill#2}\nopagebreak}
% \newcommand{\renewals}[1]{(#1 renewals)\nopagebreak}
\newcommand{\renewals}[1]{}
\newcommand{\keyskills}[1]{\vspace{10pt}Key Skills: #1.}
\newcommand{\tab}{\hspace{2em}}
\newcommand{\education}[3]{#1\tab#2\hfill#3}
\newcommand{\techstack}[1]{\textit{#1}}

\renewcommand{\familydefault}{\sfdefault} % use sans serif font

\begin{document}
%\begin{flushleft}
\setlength{\parindent}{0pt} % don't indent first line of paragraphs

\begin{center}
\LARGE{\textbf{\sc{David Bliss}}}
\end{center}

\begin{center}
London and South East England
\end{center}

\begin{center}
\href{mailto:dbliss6688@sudomail.com}{dbliss6688@sudomail.com}
\textperiodcentered\ 01274 288285
\end{center}

\begin{center}
\href{https://www.linkedin.com/in/davidbliss}{https://www.linkedin.com/in/davidbliss}
\textperiodcentered\ \href{https://github.com/blissd}{https://github.com/blissd}
\end{center}


\head{Profile}

I am a software engineer with hands-on experience creating large-scale data platforms, energy analytics algorithms, banking and insurance products, customer loyalty applications, and real-time law enforcement communication systems. I build scalable and reliable applications that can process huge datasets. Hire me today and add a practical and customer-focused member to your development team.

\head{Technical Expertise}

\begin{description}

\expertise{Core}{Scala, Kafka, Kafka Streams, Apache Spark, Kubernetes, Helm, Cassandra, AWS, big data, batch and stream processing.}

\expertise{AWS}{EMR, S3, ECR, Kinesis, Data Pipelines.}

\expertise{Languages and APIs}{Java, Python, SQL, Spring, Hibernate, JUnit, Linux.}

\expertise{Databases}{Oracle, MySQL, Mongo.}

\expertise{Messaging}{Rabbit MQ, Apache Active MQ, REST.}

\expertise{Build Tools}{sbt, Gradle, Maven, Ant, make, Jenkins, Git.}

\expertise{Methodologies}{Agile, XP, TDD, BDD.}

\end{description}

\head{Achievements}

\begin{itemize}

\item Engineered a streaming data platform processing \textbf{100,000} messages per second.

\item Implemented insurance and reinsurance capabilities to increase revenue by \textbf{\textsterling27 million per year}.

\item Reduced processing time of California's court dispositions from \textbf{60 days to 12 hours}, improving police officer safety by keeping law enforcement records up to date.

\end{itemize}

\head{Certifications}

\education{2020}{Build a TCP Chat App with Golang}{\href{https://www.udemy.com/certificate/UC-INP6UTFA}{Udemy}}

\education{2020}{Complete Guide to Protocol Buffers in Golang/Python/Java}{\href{https://www.udemy.com/certificate/UC-Q1168M4T}{Udemy}}

\education{2020}{Go: The Complete Developer's Guide}{\href{https://www.udemy.com/certificate/UC-2DGJ1LMN}{Udemy}}

\education{2020}{REST API JWT Auth with Golang}{\href{https://www.udemy.com/certificate/UC-D0WJ5R27}{Udemy}}

\education{2020}{Web Development with Golang}{\href{https://www.udemy.com/certificate/UC-1LJCOPO9}{Udemy}}

\education{2020}{gRPC Golang Master Class: Build Modern APIs and Microservices}{\href{https://www.udemy.com/certificate/UC-6F7LN2C4}{Udemy}}

\education{2020}{Learn How to Code Golang}{\href{https://www.udemy.com/certificate/UC-WX2AIINH/}{Udemy}}

\education{2019}{Programming Reactive Systems}{\href{https://courses.edx.org/certificates/3e7d7309b6d4469784d60ccccbe4562f}{edX Verified Certificate}}

\education{2017}{Blockchain for Business---An Introduction to Hyperledger Technologies}{\href{https://courses.edx.org/certificates/de3424d0c11842f48fb2c79ddf1073c8}{edX Verified Certificate}}

\education{2017}{Functional Programming in Scala Capstone}{\href{https://www.coursera.org/account/accomplishments/verify/4F5MVWUN8MWZ}{Coursera Verified Certificate}}

\education{2017}{Big Data Analysis with Scala and Spark}{\href{https://www.coursera.org/account/accomplishments/verify/BT95Z35S6LVX}{Coursera Verified Certificate}}

\education{2016}{Parallel Programming}{\href{https://www.coursera.org/account/accomplishments/verify/CJ4JSLUQK73D}{Coursera Verified Certificate}}

\education{2016}{Capstone: Retrieving, Processing, and Visualizing Data with Python}{\href{https://www.coursera.org/account/accomplishments/verify/8MKC3G5RN9S3}{Coursera Verified Certificate}}

\education{2015}{Using Databases with Python}{\href{https://www.coursera.org/account/accomplishments/verify/JNESYEJ5FURJ}{Coursera Verified Certificate}}

\education{2015}{Using Python to Access Web Data}{\href{https://www.coursera.org/account/accomplishments/verify/BVY6EDX4Z2PM}{Coursera Verified Certificate}}

\education{2015}{Python Data Structures}{\href{https://www.coursera.org/account/accomplishments/verify/VHVY2836QWWS}{Coursera Verified Certificate}}

\education{2015}{Principles of Functional Reactive Programming in Scala}{\href{https://www.coursera.org/account/accomplishments/records/8jPph3vAjsWdaQeW}{Coursera Verified Certificate}}

\education{2014}{Functional Programming Principles in Scala}{\href{https://www.coursera.org/maestro/api/certificate/get_certificate?verify-code=87DZAXY7SA}{Coursera Verified Certificate}}

\head{Career History}

\clientwork{August 2019 to January 2020}{\href{https://11fs.com/}{11:FS Foundry}}{Scala Backend Engineer}


Designed and developed microservices to support Foundry, a ledger-first API driven banking platform.
The platform was built using the Lightbend Lagom microservices framework, Scala, Cassandra, and
Kafka.\\

Designed and implemented the microservices to support the expiry of payment card authorisations. The
functionality was delivered over two sprints to support the alpha release of a new payment card
product. \\

Led the adoption of the Apache Avro message format for Kafka messages to improve performance and
reduce the risk of breaking changes to message formats.\\

\techstack{AWS, GCP, Microservices, Scala, Kubernetes, Kafka, Cassandra, Docker, Helm, Lagom, Avro.}\\

\clientwork{November 2014 to July 2019}{\href{https://www.hivehome.com}{Centrica Hive}}{Big Data Engineer}

\renewals{5}

Designed and developed pipelines with Kafka, Kakfa Streams, and Apache Spark, to implement data science algorithms to deliver customer-facing products derived from \href{https://www.hivehome.com}{Hive} thermostat data. Algorithms were packaged as Docker images and deployed with Helm charts to a Kubernetes cluster running in AWS.\\

Worked with data scientists to deliver a Kafka Streams application to analyze thermostat state, detect when a customer's heating fails, and notify the customer of that failure. A batch-based Python prototype algorithm was delivered by data scientists, but was unsuitable for real-time failure detection, so I redesigned the algorithm to work as a real-time Kafka Streams application.\\

Designed and developed a data pipeline to feed smart meter readings into algorithms to deliver energy usage insights to \href{https://www.britishgas.co.uk}{British Gas} customers. Applied a random forest, from the \href{https://www.cs.waikato.ac.nz/ml/weka/}{Weka} machine learning library, to classify customer energy usage. \\

Developed a processing pipeline tool to convert IoT device protobuf messages from an AWS kinesis stream to daily aggregated Parquet files stored in S3 and queryable from Athena.\\

\techstack{AWS, Scala, Spark, Kafka, Kafka Streams, Cassandra, Python, Kubernetes, Helm, Docker.}\\

\clientwork{August 2014 to November 2014 }{\href{http://www.postoffice.co.uk/}{Post Office}}{Developer}

Delivered a \textbf{financial reconcilliation engine} to reconcile financial transactions across Post Office products and identify transactions that cannot be balanced, and provide a reporting user interface for financial service centre staff to investigate unbalanced transactions.\\

\techstack{Java, Spring Batch, Spring Integration, Spring MVC, RabbitMQ, REST, MySQL, and Tomcat.}\\

\clientwork{January 2014 to July 2014}{\href{http://www.monitise.com/}{Monitise}}{Developer}

Developed the credit card payment user interface and backend for Yaap Shopping, a \textbf{first of its kind} venture between a telecoms company (Telef\'onica) and a bank (Santander and Caixa).  Evaluated metrics monitoring solutions for Monitise to deploy across all their platforms. For a proof-of-concept Netflix Servo was integrated as an OSGi service in the JBoss Fuse ESB.\\

\techstack{Java, Spring Web, SOAP.}\\

\clientwork{June 2012 to December 2013}{\href{http://www.aimia.com/}{Aimia}}{Developer}

\renewals{2}

Aimia is a global leader of loyalty management and owner of the \href{http://www.nectar.com/}{Nectar} brand of loyalty cards. Delivered a flexible and compelling loyalty platform to allow Aimia to \textbf{win new business}. Migrated the platform to an \textbf{event-driven architecture}. Developed a batch processing framework (Spring Batch, Mongo DB) for ingesting large files from third-party suppliers. Introduced property-based testing and BDD to \textbf{drive up code quality}.\\

\techstack{Java, Spring, Mongo DB, MySQL, Apache Camel, Rabbit MQ, AWS, REST, asynchronous events, pair programming.}\\

\clientwork{February 2011 to May 2012}{\href{http://corp.bankofamerica.com/}{Bank of America Merrill Lynch}}{Developer}

\renewals{3}

%http://www.marketwatch.com/story/bank-of-america-merrill-lynch-adds-physical-cash-concentration-to-global-liquidity-platform-2012-03-19

Delivered a \textbf{Global Liquidity Platform} that became a solid foundation for rapidly developing novel market-leading \textbf{sweeping} and \textbf{pooling} products, which included \emph{Multi-Currency Notional Pooling}, \emph{Single Currency Notional Pooling}, and \emph{\href{http://www.marketwatch.com/story/bank-of-america-merrill-lynch-adds-physical-cash-concentration-to-global-liquidity-platform-2012-03-19}{Physical Cash Concentration}}.\\

\techstack{Java, Spring, Hibernate, idempotency, compensating transactions, parallelism, pair programming.}\\

\clientwork{October 2006 to January 2011}{\href{http://www.rdfgroup.com/}{RDF Group}}{Lead Practioner}

RDF Group is a supplier of IT solutions and staff and provided my expertise to Aimia, Kiln Group, and Northern Rock.\\

\clientwork{18 months}{\href{http://www.aimia.com/}{Aimia}}{Developer and Technical Architect}

Developed a fast, flexible, and testable Java SQL templating engine. Provided training sessions for the offshore development team so they were able to take over development and provide ongoing support. Thanks to the new SQL templating system, \textbf{deadlines were met} and \textbf{financial penalties avoided}. \\

\techstack{Java, EJB3, JPA, SQL, Apache Wicket.}\\

\clientwork{9 months}{\href{http://www.tokiomarinekiln.com/}{Kiln Group}}{Developer}

Enhanced a bespoke marine insurance and reinsurance application (Java, Oracle, Swing, and EJB) to support underwriting of aviation and space business, which will earn an estimated \textbf{\textsterling27 million per year} in premiums.\\

\clientwork{2 years}{\href{http://www.northernrock.co.uk}{Northern Rock}}{Developer}

Extended and maintained an online customer mortgage Java EJB2 application.\\

\jobheld{July 2000 to July 2006}{C Squared Consulting}

Developed a fault-tolerant and \textbf{high-performance message switch} (C, BEA Tuxedo, and Oracle), which integrated the \href{http://definitions.uslegal.com/c/clets/}{California Law Enforcement Telecommunications System} with state and federal systems.\\

Lead development of California's \href{http://www.sfgate.com/cgi-bin/article.cgi?f=/c/a/2003/03/31/MN5478.DTL}{Do Not Call} system.\\

\head{Education}

\education{1996 to 2000}{2.1 BSc (with Honours) Computer Science}{University of Brighton}

\education{1994 to 1996}{Higher National Diploma in Software Engineering}{University of Brighton}

\end{document}
